Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-06-28 abstract.tex
additional fix

The goal of this work focuses on developing the necessary understanding of
potential misuse of enrichment cascades. The latter would allow more effective
international safeguards designs and approaches.  While it is straightforward to
design an enrichment cascade under ideal conditions as a function of the
theoretical feed, product and tails assays, it is very difficult to find
reliable information about the behavior of a given cascade when the feed assay
does not match the design value. Several methods have been developed to assess
the behavior of an enrichment cascade in such circumstances. In addition of the
cut ($\theta$) those methods evaluate the feed to product, feed to tails and the
product to tails enrichment ratio, respectively, $\alpha$, $\beta$ and $\gamma$,
as a function of the cascade feed assay. As those four parameters depend on each
other, determining two of them allows to fully define the other.  The first
approach consists of fixing $\theta$ and $\alpha$ recomputing the corresponding
assays at each stages of the cascade. The second one maintains the ideal
condition of the cascade ($\alpha$ and $\beta$ fixed across the whole cascade),
modifying $\theta$ value at each stage accordingly. Both approaches have been
implemented into the Cyclus fuel cycle simulator\cite{cyclus, mbmore.2018}. The
third fixes $\theta$ and $\gamma$, using both $\alpha$ and $\beta$ at each stage
as free parameters. The third method has been investigated in
\cite{walker.2017}.

>>>>

The goal of this work focuses on developing the necessary understanding of
potential misuse of enrichment cascades. The latter would allow more effective
international safeguards designs and approaches.  While it is straightforward to
design an enrichment cascade under ideal conditions as a function of the
theoretical feed, product and tails assays, it is very difficult to find
reliable information about the behavior of a given cascade when the feed assay
does not match the design value. Several methods have been developed to assess
the behavior of an enrichment cascade in such circumstances. In addition of the
cut ($\theta$) those methods evaluate the feed to product, feed to tails and the
product to tails enrichment ratio, respectively, $\alpha$, $\beta$ and $\gamma$,
as a function of the cascade feed assay. As those four parameters depend on each
other, determining two of them fully defines the other.  The first approach
consists of fixing $\theta$ and $\alpha$ recomputing the corresponding assays at
each stages of the cascade. The second one maintains the ideal condition of the
cascade ($\alpha$ and $\beta$ fixed across the whole cascade), modifying
$\theta$ value at each stage accordingly. Both approaches have been implemented
into the Cyclus fuel cycle simulator\cite{cyclus, mbmore.2018}. The third fixes
$\theta$ and $\gamma$, using both $\alpha$ and $\beta$ at each stage as free
parameters. The third method has been investigated in \cite{walker.2017}.

### 2018-06-28 experiement.tex
additional fix

\subsection{Level population}
In order to assign the optimum number of cascades to each level, a virtual cut as
been computed as:
\begin{equation}
    \theta^{v}_{j} = \frac{F_{j}-N''_{j}}{N'_{j}-N''_{j}},
\end{equation}
where, $j$ represents a level of cascade and $N_{j}$, $N'_{j}$ and $N''_{j}$
respectively the feed, product and tails assay of the cascades at this level.

A flow equation similar to \eqref{eq:flow} is then solve to get the optimum
number of cascade per level. When the tails are not recycled, the $(1-\theta)$
terms are removed from the flow equation.  The results of the level population
are summarized in Table \ref{tab:level}.

>>>>

\subsection{Level population}
In order to assign the optimum number of cascades to each level, a virtual cut as
been computed as:
\begin{equation}
    \theta^{v}_{j} = \frac{F_{j}-N''_{j}}{N'_{j}-N''_{j}},
\end{equation}
where, $j$ represents a level of cascade and $N_{j}$, $N'_{j}$ and $N''_{j}$
the feed, product and tails assay, respectively, of the cascades at this level.

A flow equation similar to \eqref{eq:flow} is then solved to obtain the optimum
number of cascade per level. When the tails are not recycled, the $(1-\theta)$
terms are removed from the flow equation.  The results of the level population
are summarized in Table \ref{tab:level}.

### 2018-06-28 theory.tex
finxing typos
additional fix

\begin{table}[htb]
\centering
\caption{Summary of the centrifuge parameters.}
\begin{tabular}{cccccccc}
\toprule
$T$[K] & $v$[m/s]    & $h$[m] & $d$[m]   & $x$   & $F$[mg/s]  & $L/F$ & $e$  \\
\midrule
320    & $320$       & $1.8$  & $0.105$  & $1^{3}$ & $13$       & 2     & 1.0  \\
\bottomrule
\end{tabular}

@@

In order to compute the proper product and tails assay at each stage, the tails
and the product from the next and the previous stage respectively must be
blended in order to determine the correct stage feed assay. All feed assays are
iteratively updated, blending the proper product and tails, then using the
updated feed assay, the new product and tails assays are recomputed. This
process is repeated until the sum of the square difference in assays is smaller
than $1^{-8}$.  As the cut remain fixed at each stage the flows do not need to
be recomputed.

@@

Using the second method, the cut value at each stage $\theta_i$, is retuned in
order to maintain the $\alpha_i$ and $\beta_i$ at their original values
(equation \eqref{eq:theta}). As the cascade remains ideal, the product and tails
assay at each stages are easily determined using equations \eqref{eq:alphabeta}.

As the cut values change, the relative flow rates between the different stage
are recomputed using equation \eqref{eq:flow}. The new flows are also
constrained by the fixed design of the cascade, number of centrifuges limiting
the flow at each level.

\subsubsection{Model C}
The last model assumes that the tails to product enrichment factor remains
constant regardless to the feed assays. To compute the response of the cascade
one need to determine $\alpha$ and $\beta$ such as their product and
$\theta$ remain fixed. 
From equations \eqref{eq:alphabeta} and the assay conservation equation $N =
\theta N' + (1-\theta)N''$ it is possible to express the product $N'$ as a function of
the feed assay $N$, $\gamma$ and the cut $\theta$ as one solution of the second
order equation \eqref{eq:gamma_p}:

>>>>

\begin{table}[htb]
\centering
\caption{Summary of the centrifuge parameters.}
\begin{tabular}{cccccccc}
\toprule
$T$[K] & $v$[m/s]    & $h$[m] & $d$[m]   & $x$   & $F$[mg/s]  & $L/F$ & $e$  \\
\midrule
320    & $320$       & $1.8$  & $0.105$  & $10^{3}$ & $13$       & 2     & 1.0  \\
\bottomrule
\end{tabular}

@@

In order to compute the proper product and tails assay at each stage, the tails
and the product from the next and the previous stage respectively must be
blended in order to determine the correct stage feed assay. All feed assays are
iteratively updated, blending the proper product and tails, then using the
updated feed assay, the new product and tails assays are recomputed. This
process is repeated until the sum of the square difference in assays is smaller
than $10^{-8}$.  As the cut remain fixed at each stage the flows do not need to
be recomputed.

@@

Using the second method, the cut value at each stage $\theta_i$, is retuned in
order to maintain the $\alpha_i$ and $\beta_i$ at their original values
(equation \eqref{eq:theta}). The cascade remaining ideal, the product and tails
assay at each stages are easily determined using equations \eqref{eq:alphabeta}.

As the cut values change, the relative flow rates between the different stage
are recomputed using equation \eqref{eq:flow}. The flow rates are determinted as
the largest flow rates allowed by the cascade design, number of centrifuges
limiting the flow at each stage.

\subsubsection{Model C}
The last model assumes that the tails to product enrichment factor remains
constant regardless to the feed assays. To compute the response of the cascade
one need to determine $\alpha$ and $\beta$ such that their product and
$\theta$ remain fixed. 
From equations \eqref{eq:alphabeta} and the assay conservation equation $N =
\theta N' + (1-\theta)N''$ it is possible to express the product $N'$ as a function of
the feed assay $N$, $\gamma$ and the cut $\theta$ as one solution of the second
order equation \eqref{eq:gamma_p}:
